\papertitle

### 2021-03-09 source_separation/paper/paper.tex
Reword conclusion section

	Furthermore, it seems that unsupervised methods, such as NMF, outperform all supervised methods tested. However, it is important to notice that the pre-trained version of the neural models (Demucs, TDCN, TDCN++ and OpenUnmix) were used. Except for TDCN++, these models were trained on musical data, yet we tested them on a wide range of targets, many of which were not strictly musical. More specifically, we may infer from our results that models trained on generic sounds generate a better separation for orchestration, as TDCN++ outperformed all other supervised models.

>>>>

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, OpenUnmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.
